---
title: "Coursera Leaflet Assignment - Week 2"
output: html_document
date: "2023-04-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

**This is a funky little interactive map of China written in Leaflet, it does the following:**

-   Merges geo map information and provincial demographic data (population)

-   Adds a legend to color code the provinces by the population density

-   Shows the name and population of the various provinces in China when you mouse hover (labels)

-   Allows you to view the Wikipedia page of the province when you click on it (popups)

```{r, echo=FALSE, message=FALSE,warning=FALSE,error=FALSE}
library(jsonlite)
library(leaflet)
library(dplyr)
library(rgdal)
require(plyr)

topoData <- rgdal::readOGR("https://raw.githubusercontent.com/deldersveld/topojson/master/countries/china/china-provinces.json", verbose=FALSE)

#get the population of the provinces
cn_prov <- read.csv('~/cnpop.csv')
cn_prov$popnum <- as.numeric(gsub(",", "", cn_prov$Population))

#create a vector for lookup
getProvincePopulation <- cn_prov$popnum
names(getProvincePopulation) <- cn_prov$Province

#create the map
topoData@data$POP <- getProvincePopulation[topoData$NAME_1]
topoData@data$label <- paste(topoData@data$NAME_1, ' - ', topoData@data$POP / 1000000, 'M')
topoData@data$link <- paste('<a target="_blank" href="https://en.wikipedia.org/wiki/', topoData@data$NAME_1,'">link</a>')

pal <- colorNumeric("viridis", NULL)

leaflet(topoData) %>%
  addTiles() %>%
  addPolygons(stroke=FALSE,
              smoothFactor = 0.3,
              fillOpacity = 1,
              fillColor = ~pal(POP),
              label = ~label,
              popup = ~link) %>%
  addLegend(pal = pal, values = ~POP, opacity = 1.0, title = "China Population")
```
